Extreme Value Chapter 3

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Figure 6 is sort of mixed with 2 now.

---
title: "Extreme Value Chapter 3"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
    self_contained: false
---

@@

```{r fig.width=12, fig.height=6}
nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         # Corrected = log_theta_stars - theta,
         Corrected = theta_bar - theta,) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  # filter(., thresh_tests < 500) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
  theme_bw()

@@

corr_a %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b

@@

# Figure 6
Compare to the GP

```{r fig.width=8, fig.height=4}

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") -> b

GP_mles %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
  theme_bw() +
  theme(legend.position = "none") -> a

```{r fig.width=8, fig.height=4}

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") +
  lims(y = c(-5, 5)) -> b

GP_mles %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
  theme_bw() +
  theme(legend.position = "none")+
  lims(y = c(-5, 5)) -> a

>>>>

---
title: "Extreme Value Chapter 3"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
---

@@

```{r eval = FALSE, fig.width=12, fig.height=6}

lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")

nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
         samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey47"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Nonparametric") +
  theme_bw(base_size = 10) -> nonpar_bxplts

par_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
         samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Parametric") +
  theme_bw(base_size = 10) -> par_bxplts

bxplts_legend <- get_legend(par_bxplts)

bxplts <- plot_grid(nonpar_bxplts+ theme(legend.position = "none"),
          par_bxplts + theme(legend.position = "none"), nrow = 2)

plot_grid(bxplts, bxplts_legend, ncol = 2, rel_widths = c(1, 0.1))

@@

corr_a %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b

@@
